HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-16 hermes_paper/hermes_paper.tex
Update Section 4

For the two metrics and for each model, we compute the average on all our sequences \numberts~  on the final year. Results are displayed in the Table~\ref{tab:metricresults}. For our model using neural networks, 10 models are trained  with different seeds. The average and the standard deviation of their results are computed and displayed. For the statistical models, TBATS largely dominate in term of MASE. It is one of the main motivations why this model is used on the best HERMES candidate as the predictor model. %However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825. \textcolor{red}{OWA dans le tableau ?}

Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slighlty outperform the alternatives in terms of MASE and are stable across the different trainings. Regarding \textit{hermes-ets},  its accuracy remains low in comparison to the \textit{lstm} benchmarck or HERMES using TBATS.

>>>>

For the two metrics and for each model, we compute the average on all our sequences \numberts~  on the final year. Results are displayed in the Table~\ref{tab:metricresults}. For our model using neural networks, 10 models are trained  with different seeds. The average and the standard deviation of their results are computed and displayed. For the statistical models, TBATS largely dominates the alternatives  in terms of MASE. It is one of the main motivations why this model is used on the best HERMES candidate as the predictor model. %However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825. \textcolor{red}{OWA dans le tableau ?}

Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slighlty outperform the alternatives in terms of MASE and are stable across the different trainings. Regarding \textit{hermes-ets},   although it is very similar to the baseline \cite{smyl2020hybrid}, its accuracy remains low in comparison to the \textit{lstm} benchmarck or HERMES using TBATS.
